Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 algorithm.tex
working on section 3

In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.  This is stated in the following pair of theorems, which together constitute our main results.

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
\end{align} 
\label{rst:budget}
\end{theorem}

\begin{theorem}
For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
is bounded above by 
\begin{align}
O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
\end{align}
\label{rst:regret}
\end{theorem}

>>>>

We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.

### 2018-02-16 result_discussion.tex
working on section 3

\section{Overview of Results and Discussion}
\dkcomment{I envision this section doing the following:
\begin{enumerate}
\item State the main theorem(s) formally.
\item Discuss lower bounds or impossibility results.
\item Discuss extensions.
\item Discuss the justification or comparison to standard bandits.
\item Discuss the comparison in the 2x2 square.
\end{enumerate}
}

\dkcomment{For now, I am just copying over material from various other
  parts that Bangrui/Peter wrote or I had written in earlier
  iterations.}

@@

\begin{theorem} \label{thm:main-overview}
Under some technical assumptions, 
there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
\dkcomment{Omitting the density here.}
\end{theorem}

>>>>

\section{Overview of Results and Discussion}

@@

%
% State the main theorem(s) formally.
%

We will show below that our algorithm (described formally below as Algorithm~\ref{alg:basic-incentivizing}) achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) + O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.  We state these results formally, which together constitute our main results.

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
\end{align} 
\label{rst:budget}
\end{theorem}

\begin{theorem}
For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
is bounded above by 
\begin{align}
O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
\end{align}
\label{rst:regret}
\end{theorem}

% Discuss lower bounds or impossibility results.
We also show a lower bound of $\Omega(\log(T))$ (section~\ref{sec:lb}) on the regret of any algorithm when agents have a density.

In the specific case of discrete distributions over agent preferences, in which $L=0$ \pfcomment{check whether this is the right description}, we obtain tighter bounds:

%Discuss extensions.

% Discuss the justification or comparison to standard bandits.
We compare these results to those possible for standard bandits. In standard bandits, the payment is obviously $0$, and the regret scales as $N \sqrt{T}$ \pfcomment{add cite}.

% Discuss the comparison in the 2x2 square.

\pfcomment{Below this is old text}
